Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-10-04 manuscript/extended_discussion.Rnw
use different figure path; remove author list

%\documentclass[english,12pt]{article}
\documentclass[5p]{elsarticle_dla}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
%\usepackage{url}
\usepackage{graphicx}
%\usepackage{rotating}
%\usepackage{wrapfig}
\usepackage{booktabs}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{setspace}
\usepackage{acronym}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
% \renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
% \renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
% \usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
%\renewcommand\cite[1]{\autocite{#1}}
%\renewcommand\citet[1]{\textcite{#1}}
% \pagestyle{fancy}

@@

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\columnwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE,cache.path="extended_discussion_cache/")
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 0)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ape")
library("ggtree")
library("topGO")
library("org.Hs.eg.db")
library("scales")
library("magrittr")
library("tidyr")
library("phytools")
@

@@

\title{The evolution of the transcriptome of mammalian placentas}%
%
\author[affigb]{Don L. Armstrong\fnref{n1}}
\ead{don@donarmstrong.com}
\author[afflon]{Michael R. McGowen\fnref{n1}}
\ead{1mmcgowen1@gmail.com}
\author[affigb]{Amy Weckle}
\ead{aweckle@illinois.edu}
\author[affwayne]{Jason Caravas}
\ead{jacaravas@gmail.com}
\author[affmich]{Dalen Agnew}
\ead{agnewd@dcpah.msu.edu}
\author[affuscd]{Kurt Benirschke}
\ead{kbenirschke@ucsd.edu}
\author[affapetrust]{Sue Savage-Rumbaugh}
\ead{suerumbaugh@gmail.com}
\author[affhaifa]{Eviatar Nevo}
\ead{nevo@research.haifa.ac.il}
\author[affnih,affwaynepath]{Chong J Kim}
\ead{cjkim@med.wayne.edu}
\author[affyale]{Günter P. Wagner}
\ead{gunter.wagner@yale.edu}
\author[affnih]{Roberto Romero}
\ead{prbchiefstaff@med.wayne.edu}
\author[affigb,affapetrust,affmip]{Derek E. Wildman\corref{cor1}}
\ead{wildmand@illinois.edu}
\cortext[cor1]{Corresponding author}
\address[affigb]{Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[afflon]{School of Biological and Chemical Sciences, Queen Mary, University of London, London, UK}
\address[affwayne]{Center for Molecular Medicine and Genetics, Wayne State University School of Medicine, Detroit, MI, USA}
\address[affmich]{Diagnostic Center for Population and Animal Health, College of Veterinary Medicine, Michigan State University, East Lansing, MI, USA}
\address[affuscd]{Department of Pathology, University of California San Diego, La Jolla, CA, USA}
\address[affapetrust]{Great Ape Trust/Bonobo Hope Sanctuary, Des Moines, IA, USA}
\address[affnih]{Perinatology Research Branch, Eunice Kennedy Shriver National Institute of Child Health and Human Development (NICHD), National Institutes of Health (NIH), Detroit, MI, USA}
\address[affwaynepath]{Department of Pathology, Wayne State University School of Medicine, Detroit, MI, USA}
\address[affyale]{Department of Ecology and Evolutionary Biology and Yale Systems Biology Institute, Yale University, New Haven, CT, USA}
\address[affmip]{Department of Molecular and Integrative Physiology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[affhaifa]{The Institute of Evolution, University of Haifa, Haifa, Israel}

\begin{abstract}
  \textbf{Background} The placenta is arguably the most
  anatomically variable organ in mammals.

  \textbf{Results} We measured the expression profiles of
  \Sexpr{star.logs[,length(unique(file))]} term placentas of
  \Sexpr{star.logs[,length(unique(species))]} species of mammals. We
  found lineage-specific differential expression of prolactin,
  relaxin, and galectins as well as increased expression of the
  pre-eclampsia associated genes \textit{ADAM12}, \textit{CRH}, and
  \textit{PAPPA} in humans. We also identified genes which are
  expressed in all placentas, including genes with immune-modulating
  properties (\textit{ANXA2}, \textit{ANXA1}, \textit{S100A11}, and
  \textit{S100A10}) and cell-cell interactions (\textit{LAMC1},
  \textit{LUM}, and \textit{LGALS1}).

  \textbf{Conclusions} A diverse array of genes are differentially
  expressed and are likely to play a role in the anatomical
  variability of the placenta in the placentas of mammalian lineages.
  Furthermore, multiple genes which are associated with pre-eclampsia
  (\textit{CRH}, \textit{ADAM12}, \textit{KISS1}, \textit{PAPPA},
  \textit{IL1RL1}, and \textit{PLAC1}) show increased expression on
  the human lineage. Still, using the strictest filtering strategy
  we find a core set of only
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  genes is essential for the proper functioning of the placenta in all
  species analyzed.

\end{abstract}

\begin{keyword}
mammal \sep  gene expression \sep evolution \sep RNA-seq \sep placenta
\end{keyword}

\maketitle

>>>>

\documentclass[english,12pt]{article}
%\documentclass[5p]{elsarticle_dla}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
%\usepackage{url}
\usepackage{graphicx}
%\usepackage{rotating}
%\usepackage{wrapfig}
\usepackage{booktabs}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{setspace}
\usepackage{acronym}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
% \renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
% \renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
% \usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
%\renewcommand\cite[1]{\autocite{#1}}
%\renewcommand\citet[1]{\textcite{#1}}
% \pagestyle{fancy}

@@

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\columnwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE,cache.path="extended_discussion_cache/")
opts_chunk$set(fig.path="extended_discussion_figure/")
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 0)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ape")
library("ggtree")
library("topGO")
library("org.Hs.eg.db")
library("scales")
library("magrittr")
library("tidyr")
library("phytools")
@

@@

\title{The evolution of the transcriptome of mammalian placentas}%

### 2016-10-04 manuscript/supplemental_material.Rnw
use different figure path; remove author list

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.6\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE,cache.path="supplemental_cache/")
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 2)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("scales")
library("gridExtra")
library("ape")
library("ggtree")
library("RSQLite")
library("topGO")
library("org.Hs.eg.db")
library("magrittr")
library("tidyr")

>>>>

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.6\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE,cache.path="supplemental_cache/")
opts_chunk$set(fig.path="supplemental_figure/")
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 2)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("scales")
library("gridExtra")
library("ape")
library("ggtree")
library("RSQLite")
library("topGO")
library("org.Hs.eg.db")
library("magrittr")
library("tidyr")
